---
title       : Data Products Assignment       
subtitle    : Just some slides to show I can work with slidify 
author      : Reza        
job         : Learn
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Summary

I used the "mtcars" dataset in R to predict the MPG of a given car based on the number of cylinders, weight and number of gears.

--- .class #id 

## Loading the data and model fitting

- First the data are added to R
```{r}
data("mtcars")
```

- Now we take a look at its first rows
```{r echo=F}
head(mtcars)
```

- From these I use 'cyl': Number of cylinders, 'wt': wight in 1000 lbs and 'gear': Number of gears for prediction.

---
## Fitting the model
- Now I fit a linear regression model with 'mpg' as regressor and 'cyl', 'wt' and 'gear' as predictors.
```{r}
fit <- lm(mpg ~ cyl + wt + gear, data = mtcars)
```

---
## Checking for the validity
- As the final step, to check the validity of the model, I draw a residual plot to see there is no special trend in residuals.

```{r echo=F, message=F, warning=FALSE, fig.height=4}
library(ggplot2)
qplot(predict(fit),resid(fit), xlab = "Fitted values", ylab = "Residuals", main = "Residual plot") + geom_hline(yintercept = 0, color="red")
```

- To use this prediction go to 

https://srhumir.shinyapps.io/Shinysimplefunction/